Output Summary

### 2022-04-21 03-post-process/output-plots.Rmd
Update residual visuals: process model quantile residuals

# function to plot a residual time series for one pop/origin/LH_type/age combo
# returns a data frame with identifiers and across-year summary statistics
plot_proc_resid = function(resid_param, sig_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract posterior samples of residual time series
  resid_post = post_subset(post, sub_index(resid_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)

  # extract posterior samples of st. dev. parameter
  sig_post = post_subset(post, sub_index(sig_param, year = year, pop = pop, origin = origin, LH_type = LH_type, age = age), matrix = TRUE)

  # divide each residual by its estimated SD parameterize: to standardize
  resid_post = apply(resid_post, 2, function(x) x/sig_post)

  # extract the year indices available
  y_ind = get_yr_index(colnames(resid_post))
  y_ind_obs = y_ind %in% observable

  # calculate posterior across-year mean and sd for each posterior sample
  # only for years that are observable; don't want to include any simulated years in these stats
  mn_post = apply(resid_post[,y_ind_obs], 1, mean)
  sd_post = apply(resid_post[,y_ind_obs], 1, sd)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(y_ind[y_ind_obs])/2)
  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
  mn_post_first = apply(resid_post[,y_first], 1, mean)
  mn_post_last = apply(resid_post[,y_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # calculate posterior summaries of standardized residual time series
  resid = apply(resid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # set the y-axis limits: want zero in center and leave room at top for legend
  ylim = max(abs(c(resid["2.5%",], resid["97.5%",])), na.rm = TRUE) * c(-1.4,1.4)

  # blank plot with correct dimensions
  par(lend = "square")
  plot(resid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", xlab = "", ylab = "")

  # draw x-axis: years
  at_x = seq(min(all_yrs[y_ind]), max(all_yrs[y_ind]), 4)
  axis(side = 1, at = at_x, labels = paste0("'", substr(at_x, 3, 4)))

  # draw the noise time series: mean and 95% CRI
  polygon(x = c(all_yrs[y_ind], rev(all_yrs[y_ind])),
          y = c(resid["2.5%",], rev(resid["97.5%",])),
          border = NA, col = alpha("salmon", 0.5))
  lines(resid["mean",] ~ all_yrs[y_ind], lwd = 2, col = "red")
  lines(resid["2.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")
  lines(resid["97.5%",] ~ all_yrs[y_ind], lty = 2, col = "red")

  # draw reference line at zero noise
  abline(h = 0, lty = 2, col = "black", lwd = 2)

@@

  # draw legend that shows estimate summaries
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  legend(x = usr[1] - xdiff * 0.05, y = usr[4] + ydiff * 0.01, legend = make_legend_text(mn_post, sd_post, first_last_mn_diff_post), bty = "n", cex = 0.8)

  # create output for building summary tables
  data.frame(param = resid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(resid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
             )

@@

```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_E_Pb_resid[year,pop]", "sig_Lphi_E_Pb[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-length-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lL_Pb_resid[year,pop]", "sig_lL_Pb[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpi_resid[year,pop]", "sig_Lpi[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Pa_Mb_resid[year,LH_type,pop]", "sig_Lphi_Pa_Mb[pop,LH_type]", pop = j, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("lDelta_L_Pb_Mb_resid[year,pop]", "sig_lDelta_L_Pb_Mb[pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Mb_Ma_resid[year,origin,pop]", "sig_Lphi_Mb_Ma[pop,origin]", pop = j, origin = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r LGR-to-BON-surv-noise, fig.width = 7, fig.height = 4}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Ma_O0_resid[year,origin]", "sig_Lphi_Ma_O0[origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_O0_O1_resid[year,origin,pop]", "sig_Lphi_O0_O1[pop]", origin = 1, year = c(1, ts_yrs), pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O1_resid[year,origin,pop]", "sig_Lpsi_O1[pop,origin]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lpsi_O2_resid[year,origin,pop]", "sig_Lpsi_O2[pop,origin]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r BON-to-LGR-surv-noise, fig.width = 7, fig.height = 4}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_resid("Lphi_Rb_Ra_resid[year,origin]", "sig_Lphi_Rb_Ra[origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_resid("Lphi_Sb_Sa_resid[year,pop]", "sig_Lphi_Sb_Sa[pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r proc-error-table-prep}
# rename parameters to human-readable format
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_resid\\[year,pop\\]", "Egg to Parr Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_resid\\[year,pop\\]", "Summer Parr Length")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_resid\\[year,pop\\]", "Migratory Strategy Apportionment")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_resid\\[year,LH_type,pop\\]", "Overwinter Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_resid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_resid\\[year,origin,pop\\]", "Trib to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_resid\\[year,origin\\]", "LGR to BON Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_resid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_resid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_resid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_resid\\[year,origin\\]", "BON to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_resid\\[year,pop\\]", "Pre-spawn Survival")

@@

# determine whether posterior of across-year quantities overlaps the target value
proc_error_ests$yr_mean_incl_zero = ifelse(proc_error_ests$year_mean_lwr <= 0 & proc_error_ests$year_mean_upr >= 0, TRUE, FALSE)
proc_error_ests$yr_sd_incl_one = ifelse(proc_error_ests$year_sd_lwr <= 1 & proc_error_ests$year_sd_upr >= 1, TRUE, FALSE)
proc_error_ests$diff_incl_zero = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_zero, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_one, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_zero, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)

>>>>

plot_proc_qresid = function(qresid_param, year = ts_yrs, pop = NULL, origin = NULL, LH_type = NULL, age = NULL, main = NULL) {

  # extract the year indices available
  y_ind = get_yr_index(colnames(qresid_post))
  y_ind_obs = y_ind %in% observable

  # calculate posterior across-year mean and sd for each posterior sample
  # only for years that are observable; don't want to include any simulated years in these stats
  mn_post = apply(qresid_post[,y_ind_obs], 1, mean)
  sd_post = apply(qresid_post[,y_ind_obs], 1, sd)

  # calculate posterior mean(last half of years) - mean(first half of years)
  y_first = 1:round(length(y_ind[y_ind_obs])/2)
  y_last = (max(y_first) + 1):length(y_ind[y_ind_obs])
  mn_post_first = apply(qresid_post[,y_first], 1, mean)
  mn_post_last = apply(qresid_post[,y_last], 1, mean)
  first_last_mn_diff_post = mn_post_last - mn_post_first

  # calculate posterior summaries of standardized qresidual time series
  qresid = apply(qresid_post, 2, function(x) c(mean = mean(x), sd = sd(x), quantile(x, c(0.5, 0.025, 0.975))))

  # blank plot with correct dimensions
  par(lend = "square")
  plot(qresid["mean",] ~ all_yrs[y_ind], main = main, type = "n",
       ylim = ylim, xlim = range(all_yrs[y_ind]), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

  # create output for building summary tables
  data.frame(param = qresid_param,
             pop = ifelse(!is.null(pop), pop, NA),
             origin = ifelse(!is.null(origin), origin, NA),
             LH_type = ifelse(!is.null(LH_type), LH_type, NA),
             age = ifelse(!is.null(age), age, NA),
             n_yrs = ncol(qresid_post[,y_ind %in% observable]),
             year_mean_mean = mean(mn_post),
             year_mean_lwr = unname(quantile(mn_post, 0.025)),
             year_mean_upr = unname(quantile(mn_post, 0.975)),
             year_sd_mean = mean(sd_post),
             year_sd_lwr = unname(quantile(sd_post, 0.025)),
             year_sd_upr = unname(quantile(sd_post, 0.975)),
             diff_mean = mean(first_last_mn_diff_post), 
             diff_lwr = unname(quantile(first_last_mn_diff_post, 0.025)), 
             diff_upr = unname(quantile(first_last_mn_diff_post, 0.975))
             )

@@

```{r egg-to-parr-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_E_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Egg-to-Parr Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r summer-length-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lL_Pb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer Parr Mean Length) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pi-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpi_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Proportion Fall Migrants) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-fall, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Fall Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r overwinter-surv-noise-spring, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Pa_Mb_qresid[year,LH_type,pop]", pop = j, LH_type = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Over-winter Survival [Spring Migrants]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r growth-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("lDelta_L_Pb_Mb_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Brood Year", "log(Summer to Spring Growth Factor) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-nor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 1, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r trib-to-LGR-surv-hor, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Mb_Ma_qresid[year,origin,pop]", pop = j, origin = 2, main = pops[j]))
oma_labels("Brood Year", "logit(Trib to LGR Survival [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r LGR-to-BON-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Ma_O0_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Brood Year", "logit(LGR to Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r yr1-ocean-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_O0_O1_qresid[year,origin,pop]", origin = 1, year = c(ts_yrs), pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(First Year Ocean Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-3-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O1_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-3 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-nor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 1, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [NOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r pr-mat-4-hor-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lpsi_O2_qresid[year,origin,pop]", origin = 2, pop = j, main = pops[j]))
oma_labels("Brood Year", "logit(Mature at Age-4 [HOR]) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r BON-to-LGR-surv-noise, fig.width = 6, fig.height = 3.5}
my_par(); par(mfrow = c(1,2))
tmp = lapply(1:jags_data$no, function(o) plot_proc_qresid("Lphi_Rb_Ra_qresid[year,origin]", origin = o, main = origins[o]))
oma_labels("Return Year", "logit(BON to LGR Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r prespawn-surv-noise, fig.width = 6, fig.height = 5}
my_par()
tmp = lapply(1:jags_data$nj, function(j) plot_proc_qresid("Lphi_Sb_Sa_qresid[year,pop]", pop = j, main = pops[j]))
oma_labels("Return Year", "logit(Pre-spawn Survival) Residual")
proc_error_ests = rbind(proc_error_ests, do.call(rbind, tmp))
```

@@

```{r proc-error-table-prep}
# rename parameters to human-readable format
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_E_Pb_qresid\\[year,pop\\]", "Egg to Parr Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lL_Pb_qresid\\[year,pop\\]", "Summer Parr Length")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpi_qresid\\[year,pop\\]", "Migratory Strategy Apportionment")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Pa_Mb_qresid\\[year,LH_type,pop\\]", "Overwinter Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "lDelta_L_Pb_Mb_qresid\\[year,pop\\]", "Summer to Spring 'Growth Factor'")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Mb_Ma_qresid\\[year,origin,pop\\]", "Trib to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Ma_O0_qresid\\[year,origin\\]", "LGR to BON Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_O0_O1_qresid\\[year,origin,pop\\]", "Yr1 Ocean Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O1_qresid\\[year,origin,pop\\]", "Pr(Mature Age-3)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lpsi_O2_qresid\\[year,origin,pop\\]", "Pr(Mature Age-4)")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Rb_Ra_qresid\\[year,origin\\]", "BON to LGR Survival")
proc_error_ests$param = stringr::str_replace(proc_error_ests$param, "Lphi_Sb_Sa_qresid\\[year,pop\\]", "Pre-spawn Survival")

@@

# determine whether posterior of across-year quantities overlaps the target value
proc_error_ests$yr_mean_incl_target = ifelse(proc_error_ests$year_mean_lwr <= 0.5 & proc_error_ests$year_mean_upr >= 0.5, TRUE, FALSE)
proc_error_ests$yr_sd_incl_target = ifelse(proc_error_ests$year_sd_lwr <= sqrt(1/12) & proc_error_ests$year_sd_upr >= sqrt(1/12), TRUE, FALSE)
proc_error_ests$diff_incl_target = ifelse(proc_error_ests$diff_lwr <= 0 & proc_error_ests$diff_upr >= 0, TRUE, FALSE)

# format the mean values to present in table
# round and make bold if target value not in interval
proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)
